The markings of the trade: exploring the patterns of olive oil production in Roman Baetica

### 2020-06-08 Paper/jaccardbaetica.tex
add correction finish draft

The distribution of amphora stamps in different \textit{conventus} can be seen in Fig. \ref{frequency}. The majority of stamps are concentrated in \textit{Hispalis} with 574 stamps while \textit{Corduba} and \textit{Astigi} with 267 and 146 stamps, respectively. Mostly, workshops show a homogeneity on the frequency of stamps except for both La Catria and Arva that exhibit a big amount of stamps with 29 different code stamps. According to previous studies, those workshops became in most important centres of amphora production although they could have more intensely prospected than others. \citep{arva_1997}.

@@

We used the same CEIPAC database as previous before to select amphora stamps, centres and coordinates. The database contained anomalies that were eliminated using the same criteria cited above. We selected the centres with more or equal than five stamps.

>>>>

The distribution of amphora stamps in different \textit{conventus} can be seen in Fig. \ref{frequency}. The majority of stamps are concentrated in \textit{Hispalis} with 574 stamps while \textit{Corduba} and \textit{Astigi} with 267 and 146 stamps, respectively. Mostly, workshops show a homogeneity on the frequency of stamps except for both La Catria and Arva that exhibit a big amount of stamps with 29 different code stamps. According to previous studies, those workshops became in most important centres of amphora production although they could have more intensely prospected than others \citep{arva_1997}.

@@

We used the same CEIPAC database as previous before to select amphora stamps, centres and geographical coordinates. The database contained anomalies that were eliminated using the same criteria cited above. We selected the centres with more or equal than five stamps.
